Report and Figures

### 2016-11-04 figs.Rmd

sub_curves %>% 
	ggplot() +
	geom_path(aes(x = nclust, y = I_XY, group = city, color = city)) +
	scale_x_continuous(trans = 'log10', limit = c(1, NA)) +
	scale_y_continuous(limit = c(0,max(sub_curves$I_XY))) +
	theme_minimal() +
  theme(text=element_text(size=16)) + 
	annotation_logticks(size = .1, sides = 'b', scaled = T) + 
	geom_rect(data = rects, aes(xmin = xmin,
								ymin = ymin,
								xmax = xmax,
								ymax = ymax,
								group = city),
			  color = 'grey',
			  alpha = 0) +
	# geom_text(aes(x = nclust, y = I_XY, label = city, hjust = -.2), data = end_points) + 
	geom_polygon(aes(nclust, I_XY, fill = city), data = filled, alpha = .2) + 
	geom_text(aes(x = 50, y = .2, label = paste('AUC = ', round(AUC,2))), data = sub_summary) + 
	# geom_text(aes(x = 50, y = .1, label = paste('J(X,Y) = ', round(J_XY,2))), data = sub_summary) +
	facet_wrap(~city) + 
  scale_fill_brewer(palette = 'Set1', name = NULL, guide = 'none') +
  scale_color_brewer(palette = 'Set1', name = NULL, guide = 'none') + 
	# scale_color_discrete(guide = F) + 
	xlab('Number of clusters') + 
	ylab('I(C,Y)') + 
	ggtitle('AUC as Clustering Evaluation')

@@

background %>% 
  ggplot(aes(x = nclust, y = I_XY)) +
  geom_path(aes(group = city), color = 'grey', alpha = 0.6) + 
  geom_path(aes(group = city, color = city), data = highlighted) +
  geom_text_repel(aes(label = city, color = city), data = end_points) +
  theme_light() +
  scale_x_continuous(trans = 'log10', limits = c(1,NA)) +
  scale_y_continuous(limits = c(0,.5)) + 
  scale_color_brewer(palette = 'Set1', name = NULL, guide = 'none') +
  xlab('Number of clusters (n)') + 
	ylab(expression(I(C[n],Y))) +
  # geom_vline(xintercept=2, alpha = .2) + 
  annotation_logticks(sides = 'b', size = .2)

>>>>

sub_curves %>% 
	ggplot() +
	geom_path(aes(x = nclust, y = I_XY, group = city, color = city)) +
	scale_x_continuous(trans = 'log10', limit = c(1, NA), expand = c(0, 0)) +
	scale_y_continuous(limit = c(0,max(sub_curves$I_XY)), expand = c(0, 0)) +
	theme_light() +
  theme(text=element_text(size=16),
        panel.margin = unit(2, "lines"),
        panel.border = element_blank(),
        strip.background = element_rect(fill = "white", color = "white", size = 2),
        strip.text.x = element_text(size = 16, color = 'black')) + 
	annotation_logticks(size = .1, sides = 'b', scaled = T) + 
	geom_rect(data = rects, aes(xmin = xmin,
								ymin = ymin,
								xmax = xmax,
								ymax = ymax,
								group = city),
			  color = 'grey',
			  alpha = 0) +
	# geom_text(aes(x = nclust, y = I_XY, label = city, hjust = -.2), data = end_points) + 
	geom_polygon(aes(nclust, I_XY, fill = city), data = filled, alpha = .2) + 
	geom_text(aes(x = 50, y = .2, label = paste('AUC = ', round(AUC,2))), data = sub_summary) + 
	# geom_text(aes(x = 50, y = .1, label = paste('J(X,Y) = ', round(J_XY,2))), data = sub_summary) +
	facet_wrap(~city) + 
  scale_fill_brewer(palette = 'Set1', name = NULL, guide = 'none') +
  scale_color_brewer(palette = 'Set1', name = NULL, guide = 'none') + 
	# scale_color_discrete(guide = F) + 
	xlab('Number of clusters (n)') + 
	ylab(expression(I(C[n],Y)))

@@

background %>% 
  ggplot(aes(x = nclust, y = I_XY)) +
  geom_path(aes(group = city), color = 'grey', alpha = 0.6) + 
  geom_path(aes(group = city, color = city), data = highlighted) +
  geom_text_repel(aes(label = city, color = city), data = end_points) +
  theme_light() +
  scale_x_continuous(trans = 'log10', limits = c(1,NA), expand = c(0, 0)) +
  scale_y_continuous(limits = c(0,.5), expand = c(0, 0)) + 
  scale_color_brewer(palette = 'Set1', name = NULL, guide = 'none') +
  xlab('Number of clusters (n)') + 
	ylab(expression(I(C[n],Y))) +
  # geom_vline(xintercept=2, alpha = .2) + 
  annotation_logticks(sides = 'b', size = .2)
